\documentclass[12pt]{article}
%\geometry{a4paper, portrait, margin=30mm, rmargin=15mm, bmargin=20mm, tmargin=20mm}

\usepackage{geometry}

\usepackage{fontspec}
\usepackage{polyglossia}
\usepackage{unicode-math}

\setmainlanguage{english}

\setmainfont{Times New Roman}
\setmathfont{Cambria Math}

\newfontfamily\Cambria{Cambria}[Scale=MatchLowercase, Ligatures=TeX]

\title{$\mathcal{L}$agrangian Kernel \\ roadmap}

\begin{document}
	\maketitle

	The unordered list of aims, plans and suggestions for $\mathcal{L}$agrangian Kernel development.

	\section{Aims}
	\begin{itemize}
		\item Replacement of old and no well architected Inner Core abstractions 
		\item Code separation that can be used by other people
	\end{itemize}

	\section{Peculiarities}

	\begin{itemize}
		\item To Do
	\end{itemize}

	\section{Future features}

	\subsection{Renderer lib (WIP)}
	To Do:

	\begin{itemize}
		\item Compile my bad code - OK
		\item Use smart pointers and make some changes for memory safety (references, const etc), in Operations class hierarchy etc - OK
		\item Test concepts of model changing operations.
		\item Realize a tessellating and a rendering.
		\item Realize a using Own texture atlas.
		\item Test concepts of model render
	\end{itemize}
	
	\subsection{Generation API (Almost not implemented)} 
	
	\begin{itemize}
		\item Replacing of all world generation.
		\item Multi biome generation.
		\item Custom Biome3D instead of native ones, with more features.
		\item GenerationFeature for generation, Biome3D for decorating and nature.
		\item Custom generation code support
	\end{itemize}

	Not in public repositories

	\subsection{Sound API (Not implemented)} 

	Blk sound

	\subsection{Micro block API (Almost not implemented)} 
	
	in GTBE REPOSITORY

	\section{Future features. Almost in other modules}

	\begin{itemize}
		\item Fields API
		\item Electromagnetic API
		\item Chemistry API
	\end{itemize}

\end{document}